oREV item selection

### 2022-11-08 analysis/irt_analysis.Rmd
add graphs and reli

@@

```{r}
dif_sex <- as_draws_df(irt1_dif_sex_sel)%>%
  select(b_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val = b_Intercept + value)%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  left_join(aoa%>%rename(item = targetWord))

@@

ggplot(dif_sex,aes(reorder(item, -aoa_german_comb), mode, ymin = lci, ymax = uci)) +
	geom_pointrange(aes(col = sex), position = position_dodge(width = .5)) +
	coord_flip() +
  scale_color_colorblind(labels = c("male","female"))+
	labs(x = "Item")+
  theme_minimal()
```

@@

>>>>

## 1PL model comparison
```{r}
loo_compare(irt1_guess, irt3_sel)%>%as_tibble(rownames = "model")

@@

```{r}
dif_sex <- as_draws_df(irt1_dif_sex_sel)%>%
  select(b_Intercept, starts_with("r_targetWord"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val =  value)%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  left_join(aoa%>%rename(item = targetWord))

@@

ggplot(dif_sex,aes(x = reorder(item, -aoa_german_comb))) +
	geom_point(aes(col = sex, y = lci), position = position_dodge(width = .5)) +
  geom_point(aes(col = sex, y = uci), position = position_dodge(width = .5)) +
  geom_linerange(aes(col = sex, ymin = lci + 0.1, ymax = uci-0.1), position = position_dodge(width = .5), alpha = .5) +
	coord_flip() +
  scale_color_colorblind(labels = c("male","female"), name = "Group")+
	labs(x = "Item", y = "Easiness estimate")+
  theme_few()
```

```{r}
ggsave("../graphs/dif_ci.png", height = 10, width = 10, scale = 1)
```

```{r}
dif_sex%>%
  pivot_wider(names_from = sex, values_from = c(mode,uci,lci))%>%
  ggplot(., aes(x = mode_f, y = mode_m))+
  geom_abline(intercept = 0, slope = 1, lty = 1, alpha = .75)+
  geom_point(pch = 1, size = 2, stroke  = 1, aes(col = factor(aoa_german_comb)))+
  geom_linerange(aes(ymin = lci_m, ymax = uci_m),  alpha = .25, lty = 1)+
  geom_linerange(aes(xmin = lci_f, xmax = uci_f),  alpha = .25, lty = 1)+
  geom_text(aes(label = item, x = uci_f +0.2))+
  labs(x = "Group: female", y = "Group: male")+
  scale_color_viridis_d()+
  guides(col = F)+
  theme_few()

```
```{r}
ggsave("../graphs/dif_cor.png", height = 8, width = 8, scale = 1.2)
```

@@

## Reliability

```{r}
rel_dat <- irt_dat%>%
  select(-sex, -order, -aoa_german_comb)%>%
  filter(targetWord %in% rasch_selected_items)%>%
  group_by(subjID)%>%
  distinct(targetWord, .keep_all = T)%>%
  pivot_wider(names_from = targetWord, values_from = correct)%>%
  ungroup()%>%
  select(-subjID)

kr20(rel_dat, hit = 1)
```

### 2022-11-08 analysis/item_selection.Rmd
add graphs and reli

rasch_fit <- irt_dat%>%
  select(-order, -sex)%>%
  filter(#targetWord %in% c("door", "jaguar","zucchini"),
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

>>>>

irt1_guess <- readRDS("../saves/irt1_guess.rds")
```

```{r}

rasch_fit <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(#targetWord %in% c("door", "jaguar","zucchini"),
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))
